Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-04-16 Paper/manuscript_v2/manuscript_07_01.tex
update 2nd paragraph of case study I

\usepackage{listings}
%\usepackage{slashbox}
\usepackage{caption}
\captionsetup{font=footnotesize}
%\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=black]{hyperref}

@@

A GP is a stochastic process which defines the distribution over a collection of random variables indexed by a continuous variable, that is, $\left\lbrace f(t): t \in \mathcal{T}\right\rbrace$ for some index set $\mathcal{T}$. GPs have the defining property that the marginal distribution of any finite subset of random variables, $\left\lbrace f(t_1), f(t_2), \hdots, f(t_K) \right\rbrace$, is a multivariate Gaussian distribution.

@@

The exact GP model for fitting this simulated dataset $\bm{y}$ can be written as follows,
%
\begin{align*}\label{ch5_eq_latentgp_simudata1}
\begin{split}
\bm{y} &= \bm{f} + \bm{\epsilon} \\
\bm{\epsilon} &\sim \Normal(0, \sigma^2  I) \\
f(x) &\sim \GP(0, k(x, x', \theta)),
\end{split}
\end{align*}
%
where $I$ represents the identity matrix and $\bm{f}=\{f(x_i)\}_{i=1}^n$ represents the underlying function values to the noisy data. The previous formulation corresponds to the latent form of a GP model. The function $f:{\rm I\!R} \to {\rm I\!R}$ is a GP prior with a Mat{\'e}rn($\nu$=3/2) covariance function $k$. Saying that the function $f(\cdot)$ follows a GP model is equivalent to say that $\bm{f}$ is multivariate Gaussian distributed with covariance matrix $\bm{K}$, where $K_{ij}=k(x_i,x_j,\theta)$, with $i,j=1,\dots,n$.

@@

The Stan model code for the approximate GP model of this case study can be found at \small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Birthday-data}.

@@

The Stan model code for the exact GP and the approximate GP models of this case study can be found at \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Leukemia-data}.
%

>>>>

\usepackage{listings}
%\usepackage{slashbox}
\usepackage{caption}
\captionsetup{font=footnotesize}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=black]{hyperref}

@@

A GP is a stochastic process which defines the distribution over a collection of random variables indexed by a continuous variable, that is, $\left\lbrace f(t): t \in \mathcal{T}\right\rbrace$ for some index set $\mathcal{T}$. GPs have the defining property that the marginal distribution of any finite subset of random variables, $\left\lbrace f(t_1), f(t_2), \hdots, f(t_N) \right\rbrace$, is a multivariate Gaussian distribution.

@@

The exact GP model for fitting this simulated dataset $\bm{y}$ can be written as follows,
%
\begin{align*}\label{ch5_eq_latentgp_simudata1}
\begin{split}
\bm{y} &= \bm{f} + \bm{\epsilon} \\
\bm{\epsilon} &\sim \Normal(0, \sigma^2  I) \\
f(x) &\sim \GP(0, k(x, x', \theta)),
\end{split}
\end{align*}
%
where $\bm{f}=\{f(x_i)\}_{i=1}^n$ represents the underlying function at the input values $x_i$, and $\bm{\epsilon}$ is the Gaussian noise term with variance $\sigma^2$, with $I$ representing the identity matrix. The previous formulation corresponds to the latent form of a GP model. The function $f:{\rm I\!R} \to {\rm I\!R}$ is a GP prior with a Mat{\'e}rn($\nu$=3/2) covariance function $k(x_i,x_j,\theta)$, which depends on the inputs $\bm{x}$ and hyperparameters $\theta=\{\alpha,\ell\}$. The hyperparameters $\alpha$ and $\ell$ represent the marginal variance and lengthscale, respectively, of the GP process. Saying that the function $f(\cdot)$ follows a GP model is equivalent to say that $\bm{f}$ is multivariate Gaussian distributed with covariance matrix $\bm{K}$, where $K_{ij}=k(x_i,x_j,\theta)$, with $i,j=1,\dots,n$.

@@

The Stan model code for the approximate GP model of this case study can be found at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Birthday-data}}.

@@

The Stan model code for the exact GP and the approximate GP models of this case study can be found at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Leukemia-data}}.
%
